---
title: "STAT 2450 Assignment 4, Winter 2019 - due February 11, at beginning of class"
author: "Yansong Li"
date: 'Banner:  B00755534'
output:
  html_document: default
  pdf_document: default
  word_document: default
---
1.  Write a function to calculate miles per gallon given kilometres travelled,
and litres of gasonline used.  The function should have two arguments, litres
and kilometres, and should return the mileage in mpg.

```{r}
mpg=function(km,litres){
   mpg=(km*5/8)/(litres/4.55)
   return(mpg)
}
mpg(100,8.3)
```

Test your function using input values of 100 kilometres and 8.3 litres.

2.  The roots of the quadratic $a x^2 + b x + c$ are given by

$$\frac{-b \pm \sqrt{b^2-4ac}}{2a}$$

If $b^2-4ac <0$, the quadratic has no real roots.

Write a function to calculate the real roots of a quadratic.  The function
should have 3 arguments, *a*, *b* and *c*.
If $b^2-4ac <0$, the function should print "quadratic has no real roots",
and then return(NULL).
Otherwise, the function should return a vector of length 2, those being
the real roots (which may be the same if  $b^2-4ac =0$).

```{r}
quadratic = function(a,b,c){
  if(b^2-4*a*c < 0){
    print("quadratic has no real roots")
    return(NULL)
  }else{
    r1 = (-b+sqrt(b^2-4*a*c))/2*a
    r2 = (-b-sqrt(b^2-4*a*c))/2*a
    result = c(r2,r1)
    return(result)
  }
}
quadratic(1,4,4)
quadratic(1,4,6)
quadratic(1,4,-6)
```

3.  Where $x_1, x_2, \ldots , x_n$ is a sample from a normal distribution
with unknown mean $\mu$ and unknown variance $\sigma^2$, the level
$100(1-\alpha)$% confidence interval for $\mu$ is given by

$$\bar x \pm t_{1-\alpha/2, n-1} \frac{s}{\sqrt n}$$

where $\bar x$ and $s$ are the sample mean and sample standard deviation
of the data, and $t_{1-\alpha/2, n-1}$ cuts off an area $1-\alpha/2$ to
its left under the $t$ curve with $n-1$ degrees of freedom.

Write a function which has two arguments, a vector of data $x$, and
and alpha, which should have a default value of .05.
The function should return
a vector of length 2, which contains the endpoints of the confidence interval.

The percentiles of the t-distrubtion can be calculated as follows. Suppose
that you want the 97.5'th percentile of the t-distribution with 23 degrees
of freedom.  This can be calculated in R as

```{r}
CI = function(x,y){
  alpha = 0.05
  if(y != alpha){alpha=y}
  x_bar = mean(x)
  s = sd(x)
  r1 = x_bar-qt(1-alpha/2,length(x)-1)*(s/sqrt(length(x)))
  r2 = x_bar+qt(1-alpha/2,length(x)-1)*(s/sqrt(length(x)))
  result = c(r1,r2)
  return(result)
}
set.seed(87612345)
data=rnorm(25,mean=4.5,sd=.75)
CI(data,0.01)
```

Test your function by calculating the 99% confidence interval using
the following data

```{r}
set.seed(87612345)
data=rnorm(25,mean=4.5,sd=.75)
```
You can check your calculation using

```{r}
t.test(data,conf.level=.99)
```


4.
The derivative of a function $f(x)$ can be approximated by the Newton's quotient

$$\frac{f(x+h) - f(x)}{h}$$

where $h$ is a small number.  Write a function to calculate the Newton's quotient
for $f(x) = exp(x)$.  The function should take two scalar arguments, $x$ and $h$.
Use a default value of $h=1.e-6$.
Test your function at the point $x=1$ using the default value of $h$, and compare
to the true value of the derivative $f'(1) = e^1$.
```{r}
quotient = function(x,h = 1.e-6){
  result = (exp(x+h)-exp(x))/h
  return(result)
}
quotient(1,1.e-6)
```

5.  A very useful feature in R is the ability to pass a function name as an argument.
Here is an example, where 2 is added to the value of a function, for three different
functions $exp(x)$, $log(x)$, and $sin(x)$, at selected points $x$.

```{r}
test=function(x,f,h = 1.e-6){
  result = (f(x+h)-f(x))/h
  return(result)
}

test(1,exp)
test(2,log)
test(pi/4,sin)
```

Modify your function from problem 4 so that you pass in the name of the function for which
you want to approximate the derivative.  Use the same default value for $h$, and approximate
the derivative of sin(x) at $x=\pi/4$, of $log(x)$ at $x=2$, and of $exp(x)$ at $x=1$.

6. 
Write a function which takes one argument $x$ of length 2, and returns the ordered
values of $x$.  That is, if $x_2<x_1$, your function should return $c(x_2,x_1)$, otherwise it
should return $x$.  (WRITE YOUR OWN FUNCTION. DO NOT USE THE BUILT IN FUNCTION ORDER)

Use your function to process a dataset with 2 columns as follows.  Iterate over the rows of the
data set, and if the element in the 2nd column of row *i* is less than the element in the first
column of row *i*, switch the order of the two entries in the row by making a suitable call to
the function you just wrote.

Test using the following data.

```{r}
set.seed(1128719)
data=matrix(rnorm(20),byrow=T,ncol=2)
compare = function(x){
  for(i in 1:nrow(x)){
    if(x[i,1] > x[i,2]){
      temp = x[i,2]
      x[i,2] = x[i,1]
      x[i,1] = temp
    }
  }
  return(x)
}
compare(data)
```

