---
title: "STAT 2450 Assignment 7, Winter 2019 - due Wednesday, March 27, at beginning of class"
author: "Yansong Li"
date: 'Banner:  B00755354'
output:
  html_document: default
  pdf_document: default
  word_document: default
---



1.  ISLR, chapter 8, problem 9.

a)

```{r}
set.seed(666)
library(ISLR)
index=sample(1:nrow(OJ),800,replace=F)
OJtrain=OJ[index,]
OJtest=OJ[-index,]

```

b)
   
```{r}
library(tree)
OJtraintree=tree(Purchase~.,data=OJtrain)
summary(OJtraintree)
```
Answer: The training error rate is 0.1625, and the tree has 9 terminal nodes.

c)
```{r}
OJtraintree
```
Answer: I pick node number 20, which is a terminal mode since it has the star sign. It has the split condition that specialCH < 0.5.
There are 67 observations in the branch with a deviance of 49.01. It is a prediction for the branch of MM.
It predicts that there are 11.94% observations has the value of MM, and 88.06% has the value of CH.

d)
```{r}
plot(OJtraintree)
text(OJtraintree)
```
Answer: Clearly, "LoyalCH" is the most important indicator since the first three splits are all about this variable.

e)
```{r}
pred_test = predict(OJtraintree, OJtest, type = "class")
table(pred_test, OJtest$Purchase)
```
Answer: The test error rate: 1-(150+76)/270 = 0.162963

f)
```{r}
cv_OJtree = cv.tree(OJtraintree, K=10, FUN = prune.tree)
cv_OJtree
```

g)
```{r}
frame = data.frame(x=cv_OJtree$size, y=cv_OJtree$dev)
plot(frame, type = 'b', xlab = "Tree size", ylab = "Deviance")
```

h)
Answer: The tree size of 9.

i)
```{r}
p_tree = prune.tree(OJtraintree, best = 5)
p_tree
```

j)
```{r}
summary(p_tree)
summary(OJtraintree)
```
Answer: The pruned tree training error rate is 0.1638, and the unpruned tree training error rate is 0.1625. Hence, the training error rate of pruned tree is higher.

k)
```{r}
pred_test1 = predict(p_tree, OJtest, type = "class")
table(pred_test1, OJtest$Purchase)
```

Answer: the test error rate of pruned tree is 1- (148 + 76)/270 = 0.17037
The test error rate of unpruned tree is 0.162963 from part d. Hence, the pruned tree test error rate is higher.

2.  ISLR, chapter 8, problem 4.   Sketch the tree (part a), and the partition of the predictor space (part b), by hand.

 The answers was finished by hand on the next page.
