---
title: "STAT 2450 Assignment 3, Winter 2019 - due February 4, at beginning of class"
author: "Yansong Li"
date: 'Banner:  B00755354'
output:
  html_document: default
  pdf_document: default
  word_document: default
---
In the following exercises, use "for" loops to do your iteration.  
(Do NOT use the built in function "sum").

1. Use a "for" loop to evaluate the following sum, when x=.5. 

$$y = \sum_{j=0}^{10} x^j$$

```{r}
y=0 # initialize y to 0
x=0.5 #initialize x to 0.5
for (i in 0:10)  {
  y = y+x^i
}
print(y)
```


Your answer should be 1.999023.

2.  Use a for loop, and the built in function "sqrt",  to do the following:

    loop over the elements of x=c(16,-9,9,4,-1,0)
    
    if the element x[i] is positive, print x[i] and the square root of x[i]
      or else if x[i] is negative, print("x[i] is negative")

```{r}
x=c(16,-9,9,4,-1,0)
for(var in x) {
   if (var>=0 ) {print(c(var,sqrt(var)))
   } else 
     {print("x[i] is negative")}
}
```

Your output should be equivalent to:

 16  4
 
 "x[i] is negative"
 
 9 3
 
 4 2
 
 "x[i] is negative"
 
 0 0


3.  Use a "for" loop to iterate over the elements of a vector x, and increment a counter
nodd when the element of x is odd.  Then print the number of even and odd elements of x.

Recall that an integer y is odd if  y%%2==1, and otherwise y is even.

Use the R commands below to generate a vector "x" of length 100.

```{r}
set.seed(10) 
x=sample(1:10,100,replace=T)
```

Then modify the following code.
```{r}
nodd=0  #initialize the counter nodd, which counts the number of odd elements of x
for (i in 1:100) {
  if(x[i]%%2==1){
    nodd=nodd+1
  } 
}
neven=length(x)-nodd   #calculate neven using the length of x and nodd.
paste("number of odd elements = ",nodd)
paste("number of even elements = ",neven)
```
For this vector x, the number of odd elements should be 56.


5.  generate a random 5x5 matrix whose entries are the numbers 1,2, ... 25, but in random positions, using the following code:
 
```{r}
set.seed(27) #set the seed for the random number generator
x=matrix(sample(1:25), byrow=T,ncol=5) #
x
```

Then, using a pair of nested for loops, loop over the positions in the
matrix x, and if the associated element of x is odd, replace the element
by its negative.

```{r}
for (i in 0:5) {
  for (j in 0:5){
    x[i,j] = ifelse(x[i,j]%%2==1, -x[i,j], x[i,j])
  }
}
print(x)
```
Your answer should be equivalent to:

  -25   -3  -21    8   -5
  
   -9    2   -1   24    4
   
   10   12   -7   20  -15
   
   22   14   18  -23  -1
   
    6   16  -19  -13  -17


